paper

### 2024-01-22 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
Edit codes for data analysis

# Create bar graphs for each age group
bar_plot <- ggplot(pivoted_table, aes(x = REPORT_YEAR)) +
  geom_bar(aes(y = Adult, fill = "Adult"), stat = "identity", position = "stack") +
  geom_bar(aes(y = Youth, fill = "Youth"), stat = "identity", position = "stack") +
  geom_bar(aes(y = Child, fill = "Child"), stat = "identity", position = "stack") +
  labs(title = "Number of Reported Crimes in Different Age Group Over the Years",
       x = "Year",
       y = "Number of reported crimes") +
  scale_fill_manual(values = c(Adult = "blue", Youth = "green", Child = "orange"),
                    name = "Age Group") +
  theme_minimal() +
  scale_x_continuous(breaks = seq(2014, 2022, by = 1))

@@

# Pivot the data to have Assault, Sexual Violation, Robbery as columns
pivoted_table <- crime_subtype_table %>%
  pivot_wider(names_from = SUBTYPE, values_from = Victims_Count, values_fill = 0)

# Print the table using knitr
kable(pivoted_table, format = "markdown", caption = "Table for Victims Count by Crime Subtype Over the Years")

@@

# Assuming 'pivoted_table' is the table with Assault, Sexual Violation, Robbery columns from the above table code

# Create bar graphs for each crime subtype
bar_plot <- ggplot(pivoted_table, aes(x = REPORT_YEAR)) +
  geom_bar(aes(y = Assault, fill = "Assault"), stat = "identity", position = "stack") +
  geom_bar(aes(y = Sexual_Violation, fill = "Sexual Violation"), stat = "identity", position = "stack") +
  geom_bar(aes(y = Robbery, fill = "Robbery"), stat = "identity", position = "stack") +
  labs(title = "Victims Count by Crime Subtype Over the Years",
       x = "Year",
       y = "Count") +
  scale_fill_manual(values = c("Assault" = "grey", "Sexual Violation" = "brown", "Robbery" = "pink"),
                    name = "Crime Subtype") +
  theme_minimal() +
  scale_x_continuous(breaks = seq(2014, 2022, by = 1))

>>>>

# Create bar graphs for each age group
bar_plot <- ggplot(pivoted_table, aes(x = REPORT_YEAR)) +
  geom_bar(aes(y = Adult, fill = "Adult"), stat = "identity", position = "stack") +
  geom_bar(aes(y = Youth, fill = "Youth"), stat = "identity", position = "stack") +
  geom_bar(aes(y = Child, fill = "Child"), stat = "identity", position = "stack") +
  labs(title = "Number of Reported Victims of Crimes in Different Age Group Over the Years",
       x = "Year",
       y = "Number of reported crimes") +
  scale_fill_manual(values = c(Adult = "blue", Youth = "green", Child = "orange"),
                    name = "Age Group") +
  theme_minimal() +
  scale_x_continuous(breaks = seq(2014, 2022, by = 1))

@@

# Pivot the data to have Assault, Sexual Violation, Robbery as columns
pivoted_table2 <- crime_subtype_table %>%
  pivot_wider(names_from = SUBTYPE, values_from = Victims_Count, values_fill = 0)

# Print the table using knitr
kable(pivoted_table2, format = "markdown", caption = "Table for Victims Count by Crime Subtype Over the Years")

@@

# Assuming 'pivoted_table2' is the table with Assault, Sexual Violation, Robbery columns from the above table code

# Create bar graphs for each crime subtype
bar_plot <- ggplot(pivoted_table2, aes(x = REPORT_YEAR)) +
  geom_bar(aes(y = Assault, fill = "Assault"), stat = "identity", position = "stack") +
  geom_bar(aes(y = `Sexual Violation`, fill = "Sexual Violation"), stat = "identity", position = "stack") +
  geom_bar(aes(y = Robbery, fill = "Robbery"), stat = "identity", position = "stack") +
  labs(title = "Victims Count by Crime Subtype Over the Years",
       x = "Year",
       y = "Number of Reported Victims of Crimes") +
  scale_fill_manual(values = c("Assault" = "grey", "Sexual Violation" = "brown", "Robbery" = "pink"),
                    name = "Crime Subtype") +
  theme_minimal() +
  scale_x_continuous(breaks = seq(2014, 2022, by = 1))

# Assuming 'crime_counts' is the data frame with relevant columns

# Filter the data for Sexual Violation
sexual_violation_data <- cleaned_data %>%
  filter(SUBTYPE == "Sexual Violation")

# Create a bar graph for Sexual Violation with groups for AGE_GROUP
bar_plot <- ggplot(sexual_violation_data, aes(x = REPORT_YEAR, y = COUNT_, fill = AGE_GROUP)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Victims Count of Sexual Violation by Age Group Over the Years",
       x = "Year",
       y = "Number of Reported Victims of Sexual Violation",
       fill = "Age Group") +
  theme_minimal() +
  scale_x_continuous(breaks = seq(min(sexual_violation_data$REPORT_YEAR), max(sexual_violation_data$REPORT_YEAR), by = 1)) +
  scale_fill_manual(values = c("Child" = "yellow", "Youth" = "orange", "Adult" = "skyblue"))
